Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-08 sas2015/content/intro.tex
removed fig 1

\input{figures/fig-transformation}

@@

We present a formalization of the transformation and prove its correctness
as follows. 
First, we derive an IDE problem that is equivalent to the original IFDS problem,
as described by Reps et al.~\cite{sagiv1996precise}.
Solving this ``Equivalence-IDE Problem'' with the IDE algorithm yields a result that
is equivalent to the one obtained by applying the IFDS algorithm to the original IFDS problem.
Then, we derive a ``Correlated-Calls 
IDE Problem'' from the original IFDS problem and show 
that the solution to this problem, when converted to an IFDS result, is more precise
than the original IFDS result.
We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
This is illustrated schematically
in Figure~\ref{fig:transformations}%
\footnote{ 
  The labels %$\resultIDE$, $\resultIFDS$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$
  on edges in 
  Figure~\ref{fig:transformations} reflect a number of mappings and projections 
  that will be defined in Section~\ref{sec:cca} and that can be ignored here.
}.

>>>>

%\input{figures/fig-transformation}

@@

We present a formalization of the transformation and prove its correctness
as follows. 
First, we derive an IDE problem that is equivalent to the original IFDS problem,
as described by Reps et al.~\cite{sagiv1996precise}.
Solving this ``Equivalence-IDE Problem'' with the IDE algorithm yields a result that
is equivalent to the one obtained by applying the IFDS algorithm to the original IFDS problem.
Then, we derive a ``Correlated-Calls 
IDE Problem'' from the original IFDS problem and show 
that the solution to this problem, when converted to an IFDS result, is more precise
than the original IFDS result.
We also show that the correlated-calls analysis is sound, i.e., that it never considers concrete execution paths as infeasible.
%This is illustrated schematically
%in Figure~\ref{fig:transformations}%
%\footnote{ 
%  The labels %$\resultIDE$, $\resultIFDS$, $\backEq$, $\backCC$, $\transEq$, and $\transCC$
%  on edges in 
%  Figure~\ref{fig:transformations} reflect a number of mappings and %projections 
%  that will be defined in Section~\ref{sec:cca} and that can be %ignored here.
%}.
